Recruiting visits to private high schools

### 2021-05-04 educ250c_presentation.Rmd
added links to 250c presentation
link

---
title: "Recruiting Chapter"
author: 
  - Ozan Jaquette
  - Crystal Han
  - Irma Castaneda
date: 
urlcolor: blue
output: 
  bookdown::html_document2:
    toc: true
    toc_depth: 2
    toc_float: true # toc_float option to float the table of contents to the left of the main document content. floating table of contents will always be visible even when the document is scrolled
      #collapsed: false # collapsed (defaults to TRUE) controls whether the TOC appears with only the top-level (e.g., H2) headers. If collapsed initially, the TOC is automatically expanded inline when necessary
      #smooth_scroll: true # smooth_scroll (defaults to TRUE) controls whether page scrolls are animated when TOC items are navigated to via mouse clicks
    number_sections: true
    fig_caption: true # ? this option doesn't seem to be working for figure inserted below outside of r code chunk
    highlight: tango # Supported styles include "default", "tango", "pygments", "kate", "monochrome", "espresso", "zenburn", and "haddock" (specify null to prevent syntax
    theme: default # theme specifies the Bootstrap theme to use for the page. Valid themes include default, cerulean, journal, flatly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti.
    df_print: tibble #options: default, tibble, paged
bibliography: ./other/burd_recruiting_chapter.bib
csl: ./other/apa.csl
---

@@

>>>>

---
title: "Recruiting visits to private high schools"
author: 
  - Ozan Jaquette
  - Crystal Han
  - Irma Castaneda
date: 
urlcolor: blue
output: 
  bookdown::html_document2:
    toc: true
    toc_depth: 2
    toc_float: true # toc_float option to float the table of contents to the left of the main document content. floating table of contents will always be visible even when the document is scrolled
      #collapsed: false # collapsed (defaults to TRUE) controls whether the TOC appears with only the top-level (e.g., H2) headers. If collapsed initially, the TOC is automatically expanded inline when necessary
      #smooth_scroll: true # smooth_scroll (defaults to TRUE) controls whether page scrolls are animated when TOC items are navigated to via mouse clicks
    number_sections: true
    fig_caption: true # ? this option doesn't seem to be working for figure inserted below outside of r code chunk
    highlight: tango # Supported styles include "default", "tango", "pygments", "kate", "monochrome", "espresso", "zenburn", and "haddock" (specify null to prevent syntax
    theme: default # theme specifies the Bootstrap theme to use for the page. Valid themes include default, cerulean, journal, flatly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti.
    df_print: tibble #options: default, tibble, paged
bibliography: ./other/burd_recruiting_chapter.bib
csl: ./other/apa.csl
---

@@

Link to html presentation

- [LINK](https://cyouh95.github.io/recruiting-chapter/educ250c_presentation.html)

Link to slides by Prof Omar Lizardo

- [LINK](https://docs.google.com/presentation/d/106TT6MHW-Fz5CmD23jZNrRbQ2wT7o07nBig0MUTSqPA/edit#slide=id.gbd14bdbd8f_0_1052)
